Appendix B: Code for analysis comparing to historical data

### 2018-11-23 appendix/appendixA.Rmd
rebuild appendices

@@

```{r optional_plotting_config, cache = FALSE, include=FALSE}
library(ggthemes)
library(ggplot2)
library(Cairo)
library(extrafont)
library(hrbrthemes)

extrafont::loadfonts()
hrbrthemes::import_roboto_condensed() 
ggplot2::theme_set(hrbrthemes::theme_ipsum_rc())

@@

```{r}
options(mc.cores=parallel::detectCores())
log_dir <- "../data/observe_harvest_recruit" # Store the computed solution files here

@@

>>>>

\pagebreak

# Setup

@@

```{r optional_plotting_config, cache = FALSE, include=FALSE}
library(ggthemes)
library(ggplot2)
library(Cairo)
library(extrafont)
library(hrbrthemes)
library(tictoc)
extrafont::loadfonts()
hrbrthemes::import_roboto_condensed() 
ggplot2::theme_set(hrbrthemes::theme_ipsum_rc())

@@

```{r}
tic()
options(mc.cores=parallel::detectCores())
log_dir <- "../data/observe_harvest_recruit" # Store the computed solution files here

@@

\pagebreak

Total runtime:

```{r}
toc()
```

Hardware:

```{r}
system2("grep", c("MemTotal", "/proc/meminfo"), stdout = TRUE)
system2('grep', '-m 1 "model name" /proc/cpuinfo', stdout = TRUE)
```

Software:

```{r}
sessionInfo()
```

\pagebreak

### 2018-11-23 appendix/appendixB.Rmd
rebuild appendices

```{r libraries, message=FALSE}
# devtools::install_github("boettiger-lab/sarsop")  ## install package first if necessary.
library(tidyverse)
library(sarsop)
library(nimble)
library(parallel)
library(gridExtra)
```

@@

>>>>

```{r libraries, message=FALSE}
# devtools::install_github("boettiger-lab/sarsop")  ## install package first if necessary.
library(tidyverse)
library(sarsop)
library(nimble)
library(parallel)
library(gridExtra)
library(tictoc)
tic()
```

@@

\pagebreak

Total runtime:

```{r}
toc()
```

Hardware:

```{r}
system2("grep", c("MemTotal", "/proc/meminfo"), stdout = TRUE)
system2('grep', '"model name" /proc/cpuinfo', stdout = TRUE)
```

Software:

```{r}
sessionInfo()
```
